Parsing Tweets into Universal Dependencies

### 2018-04-15 paper.tex
possessive citations

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that of \citet{ICWSM101540} which opted
out of splitting contractions and possessives. As a consequence of adopting \citet{ICWSM101540}'s tokenization, 
Gimpel et al.~introduced new parts of speech for these cases
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}. We therefore consider existing POS taggers for tweets instead of developing our own.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
(both greedy and CRF variants), and 
\citet{ma-hovy:2016:P16-1}'s neural network tagger 
which achieves the state-of-the-art performance on PTB.
\citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
but their implementation works only with the PTB tagset, so we exclude
it. % Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All compared systems were re-trained on the combination of the UD\_English-EWT and 
\textsc{Tweebank v2} training sets. We use Twitter-specific GloVe embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering and making use of
\citet{Brown:1992:CNG:176313.176316} clusters in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citet{ma-hovy:2016:P16-1}'s neural network
model. 
%tagger
%also makes use of clusters derived
%from a large collection of unannotated tweets. % Those clusters did not
%improve the performance of our bi-LSTM models.)

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \citet{kong-EtAl:2014:EMNLP2014}'s parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses the biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.

>>>>

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that of \citet{ICWSM101540} which opted
out of splitting contractions and possessives. As a consequence of adopting \citeposs{ICWSM101540} tokenization, 
Gimpel et al.~introduced new parts of speech for these cases
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}. We therefore consider existing POS taggers for tweets instead of developing our own.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
\citeposs{owoputi-EtAl:2013:NAACL-HLT} word cluster enhanced tagger
(both greedy and CRF variants), and 
\citeposs{ma-hovy:2016:P16-1} neural network tagger 
which achieves the state-of-the-art performance on PTB.
\Citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
but their implementation works only with the PTB tagset, so we exclude
it. % Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All compared systems were re-trained on the combination of the UD\_English-EWT and 
\textsc{Tweebank v2} training sets. We use Twitter-specific GloVe embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering and making use of
\citet{Brown:1992:CNG:176313.176316} clusters in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citeposs{ma-hovy:2016:P16-1} neural network
model. 
%tagger
%also makes use of clusters derived
%from a large collection of unannotated tweets. % Those clusters did not
%improve the performance of our bi-LSTM models.)

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \Citeposs{kong-EtAl:2014:EMNLP2014} parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses the biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.
